Master thesis problem statement: Keyword search over heterogeneous sources

### 2012-10-11 doc/thesis/latex/proposed_solutions.tex
updated problem definition, solutions and literature review. review to be finished

%%%%%  -------------------------------------------
\subsubsection*{Continuous view maintenance at Data providers with large DBs}
In the cases when new records are coming not the existing ones are not changing much, continuous view maintenance that computes only differences from earlier results could be a good solution to improve the performance.

>>>>

%%%%%  -------------------------------------------
\subsubsection*{Bad data providers performance}
In the cases when new records are coming not the existing ones are not changing much, continuous view maintenance that computes only differences from earlier results could be a good solution to improve the performance.
